The Splashback Radius of Planck-SZ clusters

### 2018-11-15 Paper_new/RSP_paper_new.tex
Minor changes in appendix

In Figure~\ref{fig:mag_errors}, we show the photometric errors of the Pan-STARRS
galaxies as a function of magnitude in each of the bands we use. The
galaxies that we use in our cross-correlation analysis for the red/blue
galaxy population have an upper absolute magnitude limit of $M_{i}-5\log h=-18.94$. This
corresponds to a different apparent magnitude limit at each redshift.
For each spectroscopically matched galaxy, we figure out how faint the
apparent magnitude limit in the $i_{\mathrm{PS}}$ band is compared to the actual
apparent magnitude of the galaxy, recorded by Pan-STARRS. Aassume that the populations of
galaxies that we use to cross-correlate with clusters have the same
intrinsic colors, but are just fainter we infer the true
intrinsic magnitude of the galaxies that we cross-correlate in the
$g_{\mathrm{PS}}$ and the $r_{\mathrm{PS}}$ band. We randomly perturb these magnitudes 
by the expected photmometric errors at that magnitude as reported in Figure~\ref{fig:mag_errors}.

Next, we compute the fraction of galaxies which were intrinsically red
that now entered the blue population by the perturbation. Where we
defined the separation of the populations using the same color
cut. We find such a contamination of intrinsically red galaxies to
the blue population to be about 5 \%. This value would apply for a galaxy population
measured in the field. Given that the red fraction is higher in clusters ($\sim
60$ \% in the whole cluster) than in the field ($\sim 40$ \%),
we expect there to be a larger proportion of red galaxies which could
potentially contaminate the blue galaxies due to photometric errors.
This would roughly double the contamination to be about 10 \%.

This is a conservative estimate of the contamination, because the
spectroscopic galaxy sample we use has a large incompleteness at the
blue end at redshifts beyond $0.2$, where SDSS targetted the luminous
red galaxy population, recording only very few blue galaxies. 
Thus we are missing a lot of the blue galaxy
population in the highest redshift bins in our spectroscopic sample.
Nevertheless we estimate if a $\sim 10$ \% contamination could
cause the splashback signal found in the cross-correlation for the blue galaxies.

>>>>

In Figure~\ref{fig:mag_errors}, we show the photometric errors of the Pan-STARRS
galaxies as a function of magnitude in each of the bands we use. The
galaxies that we use in our cross-correlation analysis for the red/blue
galaxy population have an upper absolute magnitude limit of $M_{i}-5\log h=-18.94$. This
corresponds to a different apparent magnitude limit at each redshift.
For each spectroscopically matched galaxy, we figure out how faint the
apparent magnitude limit in the $i_{\mathrm{PS}}$ band is compared to the actual
apparent magnitude of the galaxy, recorded by Pan-STARRS. Assuming that the populations of
galaxies that we use to cross-correlate with clusters have the same
intrinsic colors, but are just fainter, we infer the true
intrinsic magnitude of the galaxies that we cross-correlate in the
$g_{\mathrm{PS}}$ and the $r_{\mathrm{PS}}$ band. We randomly perturb these magnitudes 
by the expected photometric errors at that magnitude as reported in Figure~\ref{fig:mag_errors}.

Next, we compute the fraction of galaxies which were intrinsically red
that now entered the blue population by the perturbation, where we
defined the separation of the populations using the same color
cut. We find such a contamination of intrinsically red galaxies to
the blue population to be about 5 \%. This value would apply for a galaxy population
measured in the field. Given that the red fraction is higher in clusters ($\sim
60$ \% in the whole cluster) than in the field ($\sim 40$ \%),
we expect there to be a larger proportion of red galaxies in the cluster which could
potentially contaminate the blue galaxies due to photometric errors.
This would roughly double the contamination to be about 10 \%.

This is a conservative estimate of the contamination, because the
spectroscopic galaxy sample we use has a large incompleteness at the
blue end at redshifts beyond $0.2$, where SDSS targetted the luminous
red galaxy population, recording only very few blue galaxies. 
Thus we are missing a lot of the blue galaxy
population in the highest redshift bins in our spectroscopic sample.
Nevertheless we assess if a $\sim 10$ \% contamination could
cause the splashback signal found in the cross-correlation for the blue galaxies.
